%% Copyright 2013 BarD Software s.r.o
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.
\documentclass[11pt,a4paper]{moderncv-xetex}
\moderncvtheme[grey]{papeeria}
\usepackage{xcolor}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage[normalem]{ulem}
\usepackage{url}
\DeclareUrlCommand\ULurl{
  \renewcommand\UrlFont{\ttfamily\color{blue}}
  \renewcommand\UrlLeft{\uline\bgroup}
  \renewcommand\UrlRight{\egroup}}

% Header
\firstname{Kristina}\familyname{Fedorenko}
\address{}{Amsterdam, Netherlands}
\mobile{+31 6 29737202}
\email{kr.fedorenko@gmail.com}
\quote{Data scientist}

\begin{document}
\maketitle

\section{Employment}
\cventry{Mar 2012 -- Jun 2015}{Data Scientist at Adriver}{Saint Petersburg, Russia}{} \newline
    {
    Adriver is a big online advertising company which shows 2 billion banners a day. I was a member of R\&D team which was developing algorithms for detecting target audience based on user's clickstream. \\ 
    My responsibility was building data mining models which predict probability of user click on banner. The models was based on random forest, gradient boosting machine, logistic regression, Naive Bayes and so on.  
       }
    

\cventry{Jun 2015 -- Mar 2016}{Data Scientist at Data Centric Alliance}{Moscow, Russia}{} \newline
    {
     Data Centric Alliance is an online advertising startup. I was a part of the data science team which works with big data. \\ 
     Almost all the time I was working  on predicting users gender and age  by clickstream. Also I was researching algorithms and approaches for our machine learning tasks. \\ 
      \vfill
      We used
    }
    \cventry{Mar 2016 -- Feb 2017}{Data Scientist at Mail.Ru Group}{Moscow, Russia}{} \newline
    {
   Mail.Ru Group is the largest free email service in the Russian segment of the internet.  \\
   Our team and I were developing new feature for email service using machine learning.
   The feature is detecting an email category. For example, trips, purchases and so on. I developed message classifier for several categories for this feature. \\
   \vfill
   I used python, mysql, hadoop, pig for sample creation.  Vowpal wabbit and sklearn for building models. }

% ОБРАЗОВАНИЕ --------------------------------------------------------
\section{Education}
\cventry{2008\,--\,2013}{Saint Petersburg State University}{}{}\newline
    {
    The Department of Statistical Simulation \newline
    5-year degree in Applied mathematics and Computer Science. The degree is equivalent to level 7 in ISCED classification of UNESCO 2011
    }
    %
    %\cventry{Oct 2015\,--\,Dec 2015}{New Professional Laboratory}{3-month course on big data}
    %{\newline\small\url{http://newprolab.com/bigdata/eng/}}\newline
    %{During this course I've learnt a lot of things about the way hadoop and its infrastructure work. I implemented series of data classification algorithms. I got in touch with recommendation systems and even implemented some algorithms. One of the challenge about the course is that we used real-world data in our assignments and had to deal with lots of data.}
    % ДИПЛОМНАЯ РАБОТА ---------------------------------------------------
%\section{Graduation thesis}
 %   \cvline{Title}{\emph{Analysis of noise structure under different types of observation errors}}
  %  \cvline{Scientific Supervisor}{Nina Golyandina}
   % \cvline{Source}{\small \ULurl{http://tinyurl.com/fedorenko-diploma}}

% ТЕХНИЧЕСКИЕ НАВЫКИ -------------------------------------------------
\section{Professional Skills}
\cvline{Skills}{python, hive, pig, hadoop, hbase, R, awk, bash}
\cvline{Operating systems}{GNU Linux, MacOs}

% ИНОСТРАННЫЕ ЯЗЫКИ --------------------------------------------------
%\section{Additional info}
%\cvline{Languages}{English -- fluent, Russian -- native} 
%\cvline{Hobbies}{Reading, swimming}
% РЕКОМЕНДАЦИИ -------------------------------------------------------
%\section{Рекомендации}
%\cvline{А.И. Привалов}{Заведующий вычислительным центром НИИЧаВо.\newline \href{mailto:privalov@nii4avo.ru}{privalov@nii4avo.ru}}
%\cvline{А. Балаганов}{Уполномоченный по копытам ООО <<Рога и Копыта>>\newline \href{mailto:balaganov@horns-and-hooves.com}{balaganov@horns-and-hooves.com}}
%\cvline{С.М. Брин}{Computer scientist, Internet entrepreneur\newline \href{mailto:theotherboss@google.com}{theotherboss@google.com}}
\end{document}
